% !TEX encoding = UTF-8 Unicode
% !TEX root = ../Saunkin.tex

\chapter{Related work and systems} \label{c2:related-work}

The analysis of scientific citations has been an active area of research within the field of bibliometrics.
A number of metrics, data sources, and analytical approaches have been developed to assess the impact of publications and researchers.

This chapter presents an overview of the fundamental concepts and existing systems relevant to citation analysis.

\section{Data sources} \label{sec:data-sources}

Citation data is typically obtained from specialzsed academic search systems that index scientific publications and their references.

Widely used platforms are Google Scholar~\cite{googlescholar} and Semantic Scholar~\cite{semanticscholar}, which provide large-scale coverage of scientific literature and citation relationships.
These systems allow users to search for publications, track citation counts, and explore connections between works.

A relatively recent initiative, OpenAlex~\cite{openalex}, provides structured access to scholarly metadata, including citation graphs, through publicly available API.

These systems present several limitations.
Access to data is often restricted or rate limited, metadata is inconsistent across articles, and authors are not uniquely defined across data sources and publications.

\section{Existing approaches} \label{sec:existing-approaches}

Existing approaches to citation analysis primarily rely on the aggregation and examination of citation relationships between publications.

A common representation models publications as nodes in a graph, with directed edges indicating citation relationships.
This representation enables the application of graph-based methods to quantify influence among the scientific publications~\cite{Boyack2005}.

In addition to trivial citation counts, other metrics have been proposed to evaluate research impact, such as the Hirsch index (h-index)~\cite{Hirsch2005}, which attempts to capture both productivity and citation influence.

These approaches form the base of many existing citation analysis systems and are commonly used in the evaluation of scientific output.

\section{Research on self-citation} \label{sec:research-on-self-citation}

Self-citation has been discussed in the context of bibliometrics to a limited degree.

It is generally defined as a citation where at least one author appears in both the citing and cited publications~\cite{Glnzel2003BIBLIOMETRICSAA, Fowler2007, R2008ImpactReinforcing}.

Self-citations may occur naturally when researchers build upon their own previous work.
However, excessive self-citation can artificially inflate citation-based metrics and distort the perceived impact of a publication or researcher~\cite{Fowler2007, R2008ImpactReinforcing}.

Several studies have highlighted the importance of distinguishing self-citations from external citations when evaluating scientific impact.
Nevertheless, definitions and methodologies vary across studies, and many systems do not provide explicit or consistent classification~\cite{Glnzel2003BIBLIOMETRICSAA, Costas2010}.

Recent work has focused specifically on the impact of self-citations.
For example, Fiorillo (2024) introduces the Fi-score, a metric designed to assess the influence of self-citations on academic impact~\cite{Fiorillo2024}.

